---
title: "COVID 19 (INDIA & TAMILNADU) TRACKER (WIP)"
runtime: Shiny
output:
  flexdashboard::flex_dashboard:
    theme: flatly
    social: menu
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(raster)
library(readr)
library(sp)
library(jsonlite)
library(dplyr)
library(ggplot2)
library(rgeos)
library(leaflet)
library(tidyr)
library(RColorBrewer)
library(purrr)
library(plotly)

tindiadata <- read_json("https://raw.githubusercontent.com/covid19india/api/master/data.json")
indMap<-readRDS("data/indl1.rds")


statedata <- tindiadata$statewise %>% map_if(is_list, as_tibble) %>% bind_rows %>%    mutate(active=as.integer(active)) %>%
mutate(recovered=as.integer(recovered)) %>%
mutate(deaths=as.integer(deaths)) %>%
mutate(confirmed=as.integer(confirmed)) %>%
mutate(deltaconfirmed = as.integer(deltaconfirmed)) %>%
mutate(state = if_else(state == "Delhi", "NCT of Delhi", state))


tnstatedata <- filter(statedata, statecode=="TN")
indata <- filter(statedata, statecode=="TT")


confirmedColor <- "steelblue"
activeColor <- 'deeppink'
recoveredColor <- '#2C9F2C'
deathColor <- '#D62728'

```

India
=====================================================================================
Row
---------------------------------------------------------------------------------

### CONFIRMED {.value-box}

```{r}
  valueBox(
    value = paste(format(indata$confirmed, big.mark = ","), "", sep = " "),
    icon = "fas fa-user-md",
    color = confirmedColor
  )

```

### ACTIVE {.value-box}

```{r}
  valueBox(paste(format(indata$active, big.mark = ","), "", " (",
           round(100 * indata$active/indata$confirmed, 1),"%)", sep = " "),
           icon = "fas fa-ambulance",
           color = activeColor)

```

### RECOVERED {.value-box}

```{r}

valueBox(paste(format(indata$recovered, big.mark = ","), "",  " (",
         round(100 * indata$recovered/indata$confirmed, 1), "%)", sep = " "),
         icon = "fas fa-heartbeat",
         color = recoveredColor)

```

### DEATH {.value-box}
```{r}

valueBox(paste(format(indata$deaths, big.mark = ","), "", "(",
         round(100 * indata$deaths/indata$confirmed,1),"%)", sep = " "),
         icon = "fas fa-heart-broken",
         color = deathColor)

```


Row
-----------------------------------------------------------------------

### CASE DISTRIBUTION BY STATES (HOVER OVER A STATE/UT FOR MORE DETAILS)
```{r}
statecovid<-merge(indMap, statedata, by.x=c("NAME_1"), by.y=c("state"))
cp <- colorRampPalette(colors = c("White","Blue"), space="Lab")(30)
cor_cases <- colorNumeric(palette = cp,
                          domain = statecovid$cases, na.color = 'lightgrey')
statecovid %>% 
   leaflet() %>% setView(lng = 77.8047, lat = 10.7000, zoom = 4.5) %>%
     addProviderTiles('CartoDB.PositronNoLabels') %>% 
      addPolygons(color = "black", weight=1, 
                  fillColor = ~cor_cases(statecovid$active), fillOpacity=0.5,
                  highlight = highlightOptions(fillColor = "Cyan",
                                               fillOpacity = 0.8,
                                               bringToFront = TRUE),
                  group = "COVID 19 +VE Cases",
                  label=~paste0(NAME_1, " : ", active, " "), 
                  labelOptions = 
                    labelOptions(style = list("font-weight" = "normal",
                                              padding = "3px 8px"), 
                                              textsize = "15px",
                                 direction = "auto")) %>%
                  addLegend(position = "bottomleft", pal = cor_cases,
                            na.label = "No Data", 
                            values = statecovid$active,
                            title="INDIA COVID19 ACTIVE CASES", 
                            opacity = 0.8)

```

### BAR PLOT (CASE DISTRIBUTION BY STATES, TOP 25)


```{r}
statedata[-1,] %>% arrange(desc(confirmed)) %>% 
  mutate(active=as.integer(active)) %>%
  mutate(recovered=as.integer(recovered)) %>%
  mutate(deaths=as.integer(deaths)) %>%
  head(25) %>%
plotly::plot_ly(y = ~ reorder(state, active), 
          x = ~ active, 
          orientation = 'h',
          text =  ~ active,
          textposition = 'auto',
          type = "bar", 
          name = "Active",
          marker = list(color = activeColor)) %>%
  plotly::add_trace(x = ~ recovered,
            text =  ~ recovered,
            textposition = 'auto',
            name = "Recovered",
            marker = list(color = recoveredColor)) %>%
  plotly::add_trace(x = ~ deaths, 
            text =  ~ deaths,
            textposition = 'auto',
            name = "Death",
            marker = list(color = deathColor)) %>%
  plotly::layout(title = "",
         barmode = 'stack',
         yaxis = list(title = "States"),
         xaxis = list(title = "Number of Cases"),
         hovermode = "compare",
         legend = list(x = 0.65, y = 0.9),
         margin =  list(
           l = 20,
           r = 10,
           b = 10,
           t = 30,
           pad = 2
         ))

```



TamilNadu
=======================================================================================
Row
-----------------------------------------------------------------------

### CONFIRMED {.value-box}

```{r}
  valueBox(
    value = paste(format(tnstatedata$confirmed, big.mark = ","), "", sep = " "),
    icon = "fas fa-user-md",
    color = confirmedColor
  )

```

### ACTIVE {.value-box}

```{r}
  valueBox(paste(format(tnstatedata$active, big.mark = ","), "",  " (",
           round(100 * tnstatedata$active/tnstatedata$confirmed, 1), "%)", sep = " "),
           icon = "fas fa-ambulance",
           color = activeColor)

```

### RECOVERED {.value-box}

```{r}

valueBox(paste(format(tnstatedata$recovered, big.mark = ","), "", "(",
         round(100 * tnstatedata$recovered/tnstatedata$confirmed,1), "%)",  sep = " "),
         icon = "fas fa-heartbeat",
         color = recoveredColor)

```

### DEATH {.value-box}
```{r}
valueBox(paste(format(tnstatedata$deaths, big.mark = ","), "", "(",
         round(100 * tnstatedata$deaths/tnstatedata$confirmed,1), "%)", sep = " "), 
         icon = "fas fa-heart-broken",
         color = deathColor)

```



Row
-----------------------------------------------------------------------



### CASE DISTRIBUTION BY DISTRICTS (HOVER OVER A DISTRICT FOR MORE DETAILS)

```{r}
india <- readRDS('data/indl2.rds')
tn <- india[india$NAME_1=='Tamil Nadu',]
tndata <- read_csv("data/ncovid3.dat")

tncovid <- merge(tn , tndata , by.x = c("NAME_2"), by.y = c("District"))
cp <- colorRampPalette(colors = c("White","Blue"), space="Lab")(30)
cor_cases <- colorNumeric(palette = cp, domain = tncovid$Cases, na.color = 'lightgrey')                       
tncovid %>% 
  leaflet() %>% setView(lng = 77.8047, lat = 10.7000, zoom = 6.5) %>%
     addProviderTiles('CartoDB.PositronNoLabels') %>% 
     addPolygons(color = "black", weight=1, 
                 fillColor = ~cor_cases(tncovid$Cases), fillOpacity=0.5,
                 highlight = highlightOptions(fillColor = "Cyan",
                                              fillOpacity = 0.8, bringToFront = TRUE),
                 group = "COVID 19 +VE Cases",
                 label=~paste0(NAME_2, " : ", Cases, " "), 
                 labelOptions = labelOptions(style = list("font-weight" = "normal",
                                                          padding = "3px 8px"), 
                                             textsize = "15px",direction = "auto")) %>%
                 addLegend(position = "bottomleft", pal = cor_cases,
                           na.label = "No Data", 
                           values = tncovid$Cases,title="TN COVID19 +VE", opacity = 0.8)

```


### BAR PLOT (CASE DISTRIBUTION BY DISTRICTS, TOP 15)

```{r}
tndata1 <- tndata %>%  arrange(desc(Cases)) %>% head(15)
ggplot(data=tndata1, aes(x=reorder(District,Cases), y=Cases, fill = District)) + xlab("Districts") + 
geom_bar(stat="identity") + geom_text(aes(label=Cases), hjust= 0.1, position = position_dodge(width = 1))+
scale_colour_gradient2() +
coord_flip() + theme_classic() + theme(legend.position="bottom")

```




Credits
====================================================================================
<h1> Data Sources</h1>
<ul>
<li><a href="http://api.covid19india.org/">COVID 19 India API</a>
<li><a href="https://stopcorona.tn.gov.in/">TN Corona Website</a>
<li><a href="https://gadm.org/">GADM Map Data</li>
</ul>
<h1>Software Packages (WIP, TBD)</h2>
<ul>
<li><a href="https://rstudio.com/">R studio</a>
<li>Various R packages
</ul>